Scikit-learn: machine learning without learning the machinery

### 2014-11-04 article.tex
Try to address some of the comments of the editor

>>>>

Machine learning is a very active field of research, with promising
trends such as deep learning, harnessing GPUs or distributed computing
for extra computational power, or extending to new platforms, such as
Android or iOS-based embedded devises. However, as scikit-learn purpose
is to provided tried-and-true, mostly turn-key, predictive tools, we have
to walk the fine line between supporting powerful techniques and
utilizing our limited project cycles on proven technologies. For
instance, deep neural networks are an emerging tool with a huge
potential, however, they are very much a technology in flux and currently
are far from being usable with a significant expertise. Similarly, GPUs
give a lot of user-level problems, as there is a lack of binary interface
to address them uniformly and robustly over all hardwares. Finally, we
support new platforms, such as Android, as long as they come with a good
Python implementation with a standard build chain. Indeed, our basic
execution environment is the scientific Python stack, that is both very
powerful and high-level. The vision of the scikit-learn project is to
bring advances in machine learning to users that that may lack the full
expertise. As a consequence, we focus on seasoned approaches, rather than
implementing ongoing research. We believe that code is an intrinsic part
of the scholarship outcome of scientific research in computational
science \cite{buckheit1995wavelab}, and scikit-learn strives to be akin
to a reference textbook in this research software landscape.
